---
title: "segment-8"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```



```{r}
# Import and clean names

dataset <- read_csv("../data/Preliminary data_Segment8_September 25 2019.csv") %>%
  clean_names()
```


```{r}
# first vs. second half

dataset <- dataset %>%
  mutate(block_num = case_when(
         trial < 7 ~ "first",
         trial > 6 ~ "last"))


```


```{r}

ggplot(dataset, aes(x = looking_time_online_ms)) +
  geom_histogram() +
  facet_grid(trial_type ~ block_num)


```



```{r}
dataset %>%
  group_by(study_id, trial_type, block_num) %>%
  summarize(mean_looking = mean(looking_time_online_ms, na.rm = TRUE)) %>%
  group_by(block_num, trial_type) %>%
  summarize(mean_looking = mean(mean_looking, na.rm = TRUE))


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

